Self Regulation Ontology Retest Data Report

### 2018-01-19 code/SRO_Report.Rmd
updating report for draft

For this example we look at the retest reliability of the ... measures from the ... task with ... trials. Here is a graph of how the point estimates of the retest reliability changes for each of the dependent measures using different numbers of trials to estimate them.

@@

trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_icc", "score_icc"), labels = c("Accuracy", "Average RT", "Score"))))+
  geom_point()+
  geom_line()+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank())
```

>>>>

For this example we look at the retest reliability of the three dependent measures (average accuracy, median response time, total score) from the hierarchical rule task with 360 trials. Here is a graph of how the point estimates of the retest reliability changes for each of the dependent measures using different numbers of trials to estimate them. While the reliability estimate for each of the variables respectively are ..., ... and ... using all of the trials, these values are independent of number of trials used in the task for only certain variables. Based on this analysis researchers might decide to use a version of the task with fewer trials or only measures with consistently high reliability estimates.

@@

trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_icc", "score_icc"), labels = c("Accuracy", "Average RT", "Score"))))+
  geom_point()+
  geom_line()+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank())

ggsave('Intrameasure_Trialnum_Dependendence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 100)
```
